\chapter{Literature Survey}

Some of the major contributions in the optimization of BP stereo matching are as follows:
\\Chia-Kai et.al[1] used Tile based belief Propagation scheme which reduces memory
 and bandwidth and used another technique fast message construction which reduces the complexity of message construction from quadratic to linear.so it can easily parallelized.
Termination Criteria for Tile based BP are dependent on application and data so it can be possible to apply for some applications like stereo matching

Pedro F.Felzenszwalb and Daniel P.Huttenlocher [2] methods used are first distance transform technique to find new message by using cost function ,other method used are grid graph technique to update the messages.
The third technique used are multi scale algorithm to perform BP in a coarse to fine manner.These techniques are used for solving early vision problems such as stereo ,optical flow and image restoration

Li Zhou et. [3] present a general comparison survey about software and hardware processing algorithms based on algorithm inherent characteristic, implementations, and architectures

optimization potential of an Belief Propagation algorithm measured  in terms of
of speed, parallelism, data bandwidth, memory storage, etc. implemented either for  software or  for hardware
 GPU, FPGA and ASIC designs are  implemented in real-time embedded stereo vision application systems because of their high parallel processing capabilities and specific powerful calculation supporting components.
Implementing GPU has more programming flexible and powerful computational capability than FPGA and ASIC but FPGA and ASIC  have high performance, lower power consumption and cost
Stereo matching system could be enhanced along with software and hardware technology development.


Young-kyu Choi et [4] used novel memory efficient algorithm for BP in which data size and transfer bandwidth is reduced significantly by storing only part of the whole image.
In order to maintain the accuracy, the local messages are reconstructed by Graphic Processing Units (GPU) which is having advantage of available of shared memory.



Chi-Hua Lai e.tc [5] used  method of  parallelization of a belief propagation algorithm on the multicore processors  to optimize the BP  to implement on Graphic Processing Units (GPU).One of the most advanced paradigms is to apply this  technique in inferring the 3-D position of an object for stereo matching .


 Eduardo.M et.all [6] developed a FPGA implementation for depth map estimation using Belief Propagation algorithm for CAFADIS. CAFADIS IS A 3D video camera  patented  by the university of Laguna that performs depth reconstruction in real time.
The main contribution of this work is the use of FPGA technology for processing the huge amount of data



Yu-Cheng Tseng et.a[7]  worked on  a method which is  used  for stereo matching is that by partitioning an image into block and optimize with Belief Propagation. This method reduces the memory storage size with good performance.





Radu  Timofte et.al[8] studied Four-Color Theorem  on Max-product Belief propagation technique. It is used in early computer vision for solving MRF problems where energy is to be minimized

Nama et.al [9]  method used is task parallelism for Belief Propagation in acyclic graphs .The approach for task parallelism consists of constructing a task dependency graph for the input factor graph and then using a task scheduler to allocate tasks to the cores for parallel l execution,

