\begin{thebibliography}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r1}  Tappen,M.F. and Freeman,W.T., `` Comparision of graph cuts with BP for stereo,using identical MRF parameters '', \emph{In IEEE International conference on computer vision}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r2} Pedro F. Felzenszwalb,Daniel P.Huttenlocher, ``A Efficient Belief Propagation For Early Vision'', \emph{International Journal Of  Computer Science  }, Vol. 41-54, No.2, February, pp, 2006.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r3} Yu-Chang Andnelson Chang, ``Low Memory Cost Block-Based Belief Propagation For Stereo Correspondence'', \emph{IEEE Transisition}, 1-4244-1017-7187
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r4} Chia-Kai Liang,Chao-Chung Cheng,Yen-Cheieh Lai, ``A Hardware-Efficient Belief Propagation'', \emph{IEEE Transactions On Circuits And Systems For Video Technology }, Vol;21,No.5,May,pp, 2011.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r5} Li Zhou, Tao Sun, Yuanzhi Zhan and Jia Wang, ``Software and Hardware Implementations of Stereo Matching,
'', \emph{International Journal of Electronics and Informatics}, Vol.7, No.4 (2014), pp.37-562, No.1, 2014.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r6} http://nghiaho.com/notes/Markov Random Field,Loopy Belief Propagation,stereovision.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r7} Anders Olofsson,''Modern Stereo Correspondence Algorithms:Investigation and evalution'',\emph{Department of Electrocal Engineering,Linkoping University,s-581 83 Linkoping,Sweden},17 June 2010
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\bibitem{r8}J. Sun, N. N. Zheng and H. Y. Shum,"Stereo Matching Using Belief Propagation", IEEE Trans. Pattern Analysis and Machine Intelligence, vol. 7, no. 25, (2003), pp. 787-800. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\bibitem{r9}R. Szeliski, R. Zabih, D. Scharstein, O. Veksler, V. Kolmogorov, A. Agarwala, M. F. Tappen and C. Rother, "A Comparative Study of Energy Minimization Methods for Markov Random Fields", IEEE Trans. Pattern Anal. Mach. Intell., vol. 6, no. 30, (2008), pp. 1068-1080.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r10} W Freeman,E.C.,Pasztor and O.T.Carmichal, `` Learning Low level Vision '', \emph{In International  journel of computer vision},40(1);25-47,2000

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r11}Jianguo Ding,`` Probabilistic Inferences In Bayesian Networks'', \emph{International Journal Of Computer Science, Arxiv:1011.0935V2,}, 5 November 2010
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r12} Dan Yuan, ``Understanding Belief Propagation And Its Applicatons'', \emph{Department Of Computer Engineering,University Of California}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r13} Erik.B.Sudderth And William T.Freeman , ``Signal And Image Processing With Belief Propagation '', \emph{Accepted To Appear In IEEE Signal Processing Magazine},
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibitem{r14} Hany Elgala, Raed Mesleh and Harald Haas , ``Indoor Optical Wireless Communication:Potential and state of the art '', \emph{Communications Magazine, IEEE}, Vol. 49, No.9, September, pp. 56-62, 2011.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibitem{r15} Dr. Mutamed Khatib, ``Advanced Trends in Wireless Communications'', \emph{InTech}, February, 2011.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r16}Frank R.Kschischang,Brendan J.Frey,Hans Andrea Loeliger, `` Factor Graph and The Sum Product Algorithm'', \emph{IEEE Transcations On Information Theory} ,Vol 47. No.2, Feb,2001.

%http://www.visiblelightcomm.com.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r17}
http:Marl L Lrieg,`` Tutorial on Bayesian Belief Networks '', \emph{Electronics and Surveillance Research Laboratory},Australia,December ,2001.
%http://www.wikipedia.com
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r18}P. F. Felzenszwalb and D. P. Huttenlocher. Efficient belief propa-
gation for early vision. IJCV, 70(1): 41-54, 2006.

 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r19}J. S. Yedidia, W. T. Freeman, and Y. Weiss, "Generalized belief
     propagation," in Proc. NIPS, 1998, pp. 689-695.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r20}J.H.Kim and J.Pearl,'A Computational model for causal and diagnostic reasoning in inference Engines.',\emph {In proceeding on Artificial Intelligence }',Karlsruhe,West Germany,190-193,1983

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r21}J. S. Yedidia, W. T. Freeman, and Y. Weiss, "Generalized belief
     propagation," in Proc. NIPS, 1998, pp. 689-695.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
bibitem{r22}D. Scharstein and R. Szeliski. ,''A taxonomy and evaluation of dense
two-frame stereo correspondence algorithms''. IJCV, 2002.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r23} Judea Pearl, ``Probabilistic Reasoning in Intelligent Systems '', \emph{Kaufmann Morgann Publishers},Second Revised And updated Edition,San Francisco, California, 1998.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r24} https://github.com/daviddoria/Tutorials/blob/master/BeliefPropagation/-BeliefPropagation.pdf?raw=true

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{r25}http://www.cedar.buffalo.edu/srihari/CSE574/Chap8/Ch8-GraphicalModelInference/Ch8.3.3-Max-SumAlg.pdf

\bibitem{r26} Marl L Lrieg,`` Tutorial on Bayesian Belief Networks '', \emph{Electronics and Surveillance Research Laboratory},Australia,December ,2001.
%    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%\bibitem{r14} Rakesh Gupta and Amit Sharma, ``Vehicle-To-Vehicle Data Broadcasting Through Visible Light Communication'', \emph{IOSR Journal of Electronics and Communication Engineering (IOSR-JECE)}, Vol. 9, No.2, April, pp. 90-95, 2014.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\bibitem{r15}
%%http://www.visiblelightcomm.com.
\end{thebibliography} 