\chapter{Literature Survey}

The area based method [1] depends on Gestalt grouping in which support weight is based on similarity and proximity and is proportional to the strength of the grouping. In this method these two values expressed as a single value in an integrated manner. The group of similarity is calculated by means of Euclidean distance whereas group of proximity is by means of Palladian Kernel. The weight adoptive method computationally takes more time than other methods.\\
The method used in [2] is feature based local method to generate depth map or disparity map. The estimation of Disparity map is by using K-mean square algorithm and hybrid segmentation algorithm. The K means clustering algorithm is used to group the objects based on some criteria. K is a positive integer. The criteria for grouping is by minimizing the distance between data and cluster centroid .Initial set of K, virtual points in the data space randomly selected and every point if data set is assigned nearest centroid. The position of centroid is updated by means of the data points assigned to the cluster. The algorithm is stopped when minimum shift is below threshold. The segmentation algorithm extracts feature by Scale Invariant Feature Transform (SIFT) and Sum of Absolute Difference (SAD).The proposed algorithm is complex and computation time is more.
%
The major contribution in the field of stereo matching using Random Markov field and inference algorithm like Belief Propagation.
2003 Comparison of Graph cuts with Belief Propagation for stereo, Using Identical MRF Parameters:
The disparity image can be achieved by modeling Markov Random Field and by using optimization algorithm such as Graph cut and Belief Propagation. These two algorithm allow fast and approximate solution to MRF which are powerful tools for modeling vision problems.so one system improvement over the other be attributed to its choice of an inference algorithm.
The comparison between Graph cut algorithm with max product Belief Propagation algorithm shows that the solution for energy by Graph cut and Belief Propagation algorithm nearly equal although graph cut consistently returns smaller energy. The solutions produced by Graph cut are smoother while accelerated Belief Propagation algorithm was faster.
Given this situation improving formulation of MRF rather than improving solution (optimization algorithm) for MRF.
The comparisons between inference algorithm such as Graph cut and Belief Propagation depends on the functions of MRF formulation.\\
The future research can be different functions such as truncated linear or quadratic used for MRF optimizing with any one of the inference algorithm\\
2004 Efficient Belief Propagation for Early Vision:
The early vision problems such as stereo, optical flow and image restoration can be solved by MRF model by using inference algorithm based on Graph cut and Belief propagation in this paper new algorithm techniques improve the running time of the algorithm.
The inference algorithm used is max product belief propagation.\\
The three techniques substantially reduce time required to compute the message updates.
\begin{enumerate}
  \item {In low level vision problems the label or hidden node is generally based on some difference between two labels rather than on particular pair of labels, this is known as distance transform technique. This technique reduces message computing time.}

  \item {In new message update scheme, here nodes are split into two
Messages are updated alternately, so half of the messages only updated at each iteration.so memory required to store messages are reduced}
  \item {The third technique uses hierarchical structure to reduce the number of message passing iterations to small constant rather depends on size of the image grid.}
\end{enumerate}


2007  Low Memory Cost Block Based Belief Propagation for Stereo Correspondence

The global approaches can handle the texture less and occluded regions well by formulating disparity inference as an energy minimization problem. The energy function usually has smoothness constraint which represents a certain relationship between neighboring pixel pair. This smoothness constraint enforces penalty on the energy function, if the labels (disparity or segments) of neighboring pixel are inconsistent.
The 2D optimization algorithm such as graph cut and Belief Propagation have been applies successfully to optimize energy functions. The BP algorithms construct 2-D graph structures with nodes represent all pixels in the disparity image to find the disparity map with energy closer to the global minima. However, the vast number of nodes in 2-D graph result in extremely high computation complexity too difficulty in real time applications.
The proposed Block based Belief Propagation algorithm directly partitions image into separated independent blocks.so memory size reduces significantly due to block based computation. With block based design, the criterion of convergence becomes important for each block. In general, the criterion of convergence in belief propagation is defined with the saturation of energy functions. The specific threshold is set to terminate the belief propagation process. However it is difficult to find a global threshold for each block. In proposed algorithm find the convergence according to the equivalence of all disparities for each node in a block over successive iterations.\\
2009 Hardware-Efficient Belief Propagation
Loopy belief propagation is an effective solution for assigning labels to the nodes of a graphical model such as Markov Random Field, but requires high memory, bandwidth and computational costs.
In this paper two techniques are proposed
\begin{enumerate}
  \item {Tile based Belief propagation ,when message is updated data of nodes which are far away are not required, so MRF is divided into
Multiple regions known as tile and iterations are done on those regions. So memory required to store messages are reduced}
  \item {Fast message construction:The cost functions serve for measuring the compatibility between the labels and the observations or prior knowledge.
For example in stereo matching that the disparity values vary smoothly between neighboring pixels. However this assumption is valid only when corresponding pixels belong to the same object. Otherwise the difference between their disparity values can be arbitrarily large resulting high cost value. In fast message construction using robust function is used as smoothness cost.}
\end{enumerate}
	


